---
output:
  word_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(tidymodels)
library(e1071)
library(ROCR)
```

```{r}
parole = read_csv("parole.csv")
```

```{r}
str(parole)
summary(parole)
```

## Carefully convert the male, race, state, crime, multiple.offenses, and violator variables to factors.
## Recode (rename) the factor levels of each of these variables according to the description of the variables provided in the ParoleData.txt file (located with the assignment on Canvas).

```{r}
parole = parole %>% mutate(male = as_factor(male)) %>% mutate(male = fct_recode(male, "female" = "0", "male" = "1")) %>% 
  mutate(race = as_factor(race))%>% mutate(race = fct_recode(race, "otherwise" = "2", "white" = "1")) %>% 
  mutate(age = as_factor(age)) %>%
  mutate(state = as_factor(state))%>% mutate(state = fct_recode(state, "other" = "1", "Kentucky" = "2", "Louisiana" = "3", "Virginia" = "4")) %>%
  mutate(time.served = as_factor(time.served)) %>%
  mutate(max.sentence = as_factor(max.sentence)) %>%
  mutate(multiple.offenses = as_factor(multiple.offenses)) %>% mutate(multiple.offenses = fct_recode(multiple.offenses, "otherwise" = "0", "multiple" = "1")) %>% 
  mutate(crime = as_factor(crime)) %>% mutate(crime = fct_recode(crime, "other" = "1", "larceny" = "2", "drug" = "3", "driving" = "4")) %>% 
  mutate(violator = as_factor(violator)) %>% mutate(violator = fct_recode(violator, "no" = "0", "yes" = "1"))
```


## There are 675 parolees in the dataset. How many of these parolees ended up violating parole? HINT: Examine the response variable “violator”.

```{r}
violated.parole = parole %>% filter(violator %in% c("no"))

```

##  Split the data into training and testing sets. Your training set should have 70% of the data. Use a random number (set.seed) of 12345. Be sure that the split is stratified by “violator”

```{r}
set.seed(12345)
parole_split = initial_split(parole, prop = .70, strata = violator)
train = training(parole_split)
test = testing(parole_split)

```


## Second part of question 2. I was supposed to use "yes" and "no" instead of "completed" and "violated". "Yes" would have been the positive class/category. In this case, since I used other terms, it would be "completed", which would be our positive class. I ended up changing that part to follow the rules.
```{r}
levels(train$violator)

train = train %>% mutate(violator = fct_relevel(violator, c("no","yes")))
levels(train$violator)

```

```{r}
parole_model = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm")

parole_recipe = recipe(violator~state, train) 

logreg_wf =
  workflow() %>%
  add_model(parole_model) %>%
  add_recipe(parole_recipe)

parole_fit = fit(logreg_wf, train)

```


```{r}

summary(parole_fit$fit$fit$fit)
```

```{r}
parole_model2 = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm")

parole_recipe2 = recipe(violator~state + multiple.offenses + race, train) 

logreg_wf2 =
  workflow() %>%
  add_model(parole_model2) %>%
  add_recipe(parole_recipe2)

parole_fit2 = fit(logreg_wf2, train)
```

```{r}
summary(parole_fit2$fit$fit$fit)
```


```{r}
newdata = data.frame(state = "Louisiana", multiple.offenses = "multiple", race = "white")
predict(parole_fit2,newdata,type="prob")
```



```{r}
newdata = data.frame(state = "Louisiana", multiple.offenses = "multiple", race = "white")
predictions = predict(parole_fit2, parole, type = "prob")

predict(parole_fit2, newdata, type = "prob")
```
```{r}
predictions = predict(parole_fit2, train, type = "prob")[2]
head(predictions)
```

```{r}
ROCRpred = prediction(predictions, train$violator)

ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-.2,1.7))
```



```{r}
as.numeric(performance(ROCRpred,"auc")@y.values)
```


```{r}
opt.cut = function(perf,pred){
  cut.ind = mapply(FUN=function(x,y,p){
    d=(x-0)^2+(y-1)^2
    ind=which(d==min(d))
    c(sensitivity=y[[ind]], specificity=1-x[[ind]],
      cutoff=p[[ind]])
  },perf@x.values,perf@y.values,pred@cutoffs)
}
print(opt.cut(ROCRperf,ROCRpred))
    
```


```{r}
t1 = table(train$violator,predictions > .2015788)
t1
```

```{r}
(t1[1,1]+t1[2,2])/nrow(train)
```
## Sensitivity
```{r}
36 / (18+36)
```
## Specificity
```{r}
360 / (360 + 57)  
```



```{r}
nrow(train)
```

```{r}
t2 = table(train$violator,predictions > .5)

(t2[1,1]+t2[2,2])/nrow(train)
```

