

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)

```

```{r}
air = airquality
```


## How many rows are in the "air" dataframe?

```{r}
nrow(air)
```

## How many columns are in the “air” dataframe?

```{r}
dim(air)
```

```{r}
air2 = air %>% drop_na()
```

## How many rows remain in this new (air2) data frame?

```{r}
nrow(air2)
```

## How many columns remain in this new (air2) data frame?

```{r}
dim(air2)
```

## Which variable is most strongly correlated with the “Ozone” variable?
## Which variable is least strongly correlated with the “Ozone” variable?

```{r}
ggpairs(air2)
```

```{r}
ggcorr(air2, label = TRUE)
```


## Plot “Temp” (x axis) versus “Ozone” (y axis) using the “ggplot” function. Choose an appropriate chart type. Which statement best describes the relationship between “Temp” and “Ozone”?

```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point(alpha=0.5)+
  theme_bw()
```




```{r}

air2_simple = recipe(Temp ~ Ozone, air2)

lm_model = 
  linear_reg() %>%
  set_engine("lm")

lm_wflow = 
  workflow() %>%
  add_model(lm_model)%>%
  add_recipe(air2_simple)

lm_fit = fit(lm_wflow, air)

summary(lm_fit$fit$fit$fit)
```

## Use the code below to generate 95% confidence intervals for the coefficients. Note that you may need to change “lm_fit” to the name of your model fit if you used a different name. True/False: A 95% confidence interval for the slope coefficient does not contain zero

```{r}
confint(lm_fit$fit$fit$fit)
```

## Using your linear regression model with “Temp” to predict “Ozone”, what is the predicted “Ozone” value when “Temp” is equal to 80 (to two decimal places)
```{r}
69.41072 + 0.20081 * 80

testdata <- data.frame(Ozone = c(80))
predict(lm_fit, new_data = testdata)
```


```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()+
    geom_smooth(method = "lm", se=FALSE, color="red")+ theme_bw()
```

```{r}
dwtest(lm_fit$fit$fit$fit)
```

